Predator clusters

### 2024-05-30 reports/01_predators.qmd
Final commit before Zenodo preparations

# Make the map! 
ant_basemap() +
  geom_spatraster(data = topsix_clim_class) +
  geom_sf(data = ant_sf) +
  scale_fill_brewer(palette = "RdPu", 
                    na.value = NA, 
                    direction = 1,
                    na.translate = FALSE) +
  scale_x_continuous(breaks = seq(-64, -54, by = 4)) +
  scale_y_continuous(breaks = seq(-64, -59, by = 2)) +
  labs(fill = expression("Ind km"^-1)) +
  facet_wrap(~lyr) +
  coord_sf(xlim = map_bbox[1:2],
           ylim = map_bbox[3:4],
           crs = ant_proj()) +
  theme(legend.position = "top")

>>>>

# Make the map! 
sublabels <- tibble(lyr = names(topsix_clim_class),
                    x = -62.25, y = -59.25) %>% 
  arrange(lyr) %>% 
  mutate(labels = LETTERS[1:6]) %>% 
  st_as_sf(crs = "EPSG:4326", coords = c("x", "y"))
p <- ant_basemap() +
  geom_spatraster(data = topsix_clim_class) +
  geom_sf(data = ant_sf) +
  geom_sf_text(aes(label = labels), sublabels, fontface = "bold") +
  scale_fill_brewer(palette = "RdPu", 
                    na.value = NA, 
                    direction = 1,
                    na.translate = FALSE) +
  scale_x_continuous(breaks = seq(-64, -54, by = 4)) +
  scale_y_continuous(breaks = seq(-64, -59, by = 2)) +
  labs(fill = expression("Ind km"^-1)) +
  facet_wrap(~lyr) +
  coord_sf(xlim = map_bbox[1:2],
           ylim = map_bbox[3:4],
           crs = ant_proj()) +
  theme(legend.position = "top",
        panel.background = element_rect(color = "grey20"),
        strip.text = element_blank())
ggsave(here::here("figs/Figure 2.eps"), p, 
       width = 169, height = 121, units = "mm")
p

### 2024-05-30 reports/04_pred_clus.qmd
Final commit before Zenodo preparations

ant_basemap() +
  # Sea ice
  geom_tile(aes(x, y, fill = seaice_conc), 
            filter(seaice_conc_df, between(seaice_conc, 0.65, 1)),
            alpha = 0.8) +
  scale_fill_distiller(lim = c(0.65, 1),
                       palette = "Blues",
                       na.value = "transparent") +
  # Predator clusters
  ggnewscale::new_scale_fill() +
  geom_sf(aes(fill = pred_clust), 
          stations_clust, 
          size = 2, 
          shape = 22) +
  facet_wrap(~ Year) +
  scale_x_continuous(breaks = c(-60, -55)) +
  scale_y_continuous(breaks = c(-63, -62, -61, -60)) +
  scale_fill_brewer(palette = "Dark2") +
  guides(fill = guide_legend(override.aes = list(size = 3))) +
  coord_ant(map_lim) +
  theme(legend.position = "bottom",
        legend.title = element_blank())
```

@@

ant_basemap() +
  # Predator clusters
  ggnewscale::new_scale_fill() +
  geom_sf(aes(color = pred_clust,
              linetype = contlabel), 
          cluster_kde, 
          fill = NA,
          linewidth = 1) +
  facet_wrap(~ pred_clust) +
  scale_x_continuous(breaks = c(-60, -55)) +
  scale_y_continuous(breaks = c(-63, -62, -61, -60)) +
  scale_color_brewer(palette = "Dark2") +
  scale_linetype_manual(values = c(2, 1), guide = "none") +
  coord_ant(map_lim) +
  theme(legend.position = "bottom",
        legend.title = element_blank())
```

@@

  ggplot(nmds_df, aes(.data[[x]], .data[[y]])) +
    stat_contour(aes(z = .data$ice_coverage, 
                     color = after_stat(level)),
                 ice_df) +
    scale_color_distiller(
      "Ice coverage",
      palette = "Blues",
      labels = scales::percent,
      limits = c(0.25, 0.75),
      breaks = seq(0.25, 0.75, by = 0.1),
      guide = guide_colorbar(barwidth = unit(2, "in"),
                             direction = "horizontal")
    ) +
    ggnewscale::new_scale_color() +
    geom_point(aes(color = pred_clust), alpha = 0.8) +
    geom_point(data = year_centroids, 
               shape = 18,
               size = 2.5,
               color = "black",
               alpha = 0.85) +
    ggrepel::geom_text_repel(aes(label = Year),
                             year_centroids) +
    scale_color_brewer(
      palette = "Dark2",
      guide = guide_legend(override.aes = list(size = 2),
                           direction = "horizontal",
                           order = 1)
    ) +
    labs(color = "Predator cluster") +
    theme_classic()
}

map2(c(1, 1, 2), c(2, 3, 3), nmds_plot) %>% 
  reduce(`|`) +
  plot_annotation(tag_levels = 'A') +
  plot_layout(guides = "collect") &
    theme(legend.position = "bottom",
          legend.direction = "horizontal",
          plot.tag = element_text(face = "bold"))
```

@@

ggplot(stations_clust, 
       aes(x = ice_coverage / 10, fill = after_stat(x))) + 
  geom_histogram(bins = 20, color = "grey30") +
  geom_vline(aes(xintercept = median_ice),
             median_coverge,
             color = "red", linetype = "dashed") +
  scale_x_continuous(labels = scales::percent) +
  scale_fill_distiller(palette = "Blues", guide = NULL) +
  facet_grid(rows = vars(pred_clust)) +
  labs(x = "Ice coverage",
       y = "# sites") +
  theme_minimal()

>>>>

sublabels <- tibble(Year = 2012:2016,
                    x = -63, y = -60,
                    labels = LETTERS[1:5]) %>% 
  st_as_sf(crs = "EPSG:4326", coords = c("x", "y"))
p <- ant_basemap() +
  # Sea ice
  geom_tile(aes(x, y, fill = seaice_conc), 
            filter(seaice_conc_df, between(seaice_conc, 0.65, 1)),
            alpha = 0.8) +
  scale_fill_distiller("Ice concentration",
                       lim = c(0.65, 1),
                       labels = scales::percent,
                       palette = "Blues",
                       na.value = "transparent",
                       guide = guide_colorbar(title.position = "top")) +
  # Predator clusters
  ggnewscale::new_scale_fill() +
  geom_sf(aes(fill = pred_clust), 
          stations_clust, 
          size = 2, 
          shape = 22) +
  facet_wrap(~ Year) +
  # Labels
  geom_sf_text(aes(label = labels), sublabels, fontface = "bold", vjust = 0) +
  scale_x_continuous(breaks = c(-60, -55)) +
  scale_y_continuous(breaks = c(-63, -62, -61, -60)) +
  scale_fill_brewer("Predator cluster", palette = "Dark2",
                    guide = guide_legend(override.aes = list(size = 3),
                                         title.position = "top")) +
  coord_ant(map_lim) +
  theme(legend.position = "bottom",
        strip.text = element_blank(),
        panel.background = element_rect())

ggsave(here::here("figs/Figure 4.eps"), p, 
       width = 169, height = 121, units = "mm")
p
```

@@

sublabels <- tibble(pred_clust = factor(levels(cluster_kde$pred_clust)),
                    x = -63, y = -60,
                    labels = LETTERS[1:3]) %>% 
  st_as_sf(crs = "EPSG:4326", coords = c("x", "y"))
p <- ant_basemap() +
  # Predator clusters
  ggnewscale::new_scale_fill() +
  geom_sf(aes(color = pred_clust,
              linetype = contlabel), 
          cluster_kde, 
          fill = NA,
          linewidth = 1) +
  geom_sf_text(aes(label = labels), sublabels, fontface = "bold", vjust = 0) +
  facet_wrap(~ pred_clust) +
  scale_x_continuous(breaks = c(-60, -55)) +
  scale_y_continuous(breaks = c(-63, -62, -61, -60)) +
  scale_color_brewer("Predator cluster", palette = "Dark2") +
  scale_linetype_manual(values = c(2, 1), guide = "none") +
  coord_ant(map_lim) +
  theme(legend.position = "bottom",
        strip.text = element_blank(),
        panel.background = element_rect())

ggsave(here::here("figs/Figure 5.eps"), p, 
       width = 169, height = 57, units = "mm")
p
```

@@

  ggplot(nmds_df, aes(.data[[x]], .data[[y]])) +
    stat_contour(aes(z = .data$ice_coverage, 
                     color = after_stat(level)),
                 ice_df) +
    scale_color_distiller(
      "Ice coverage",
      palette = "Blues",
      labels = scales::percent,
      limits = c(0.25, 0.75),
      breaks = seq(0.25, 0.75, by = 0.1),
      guide = guide_colorbar(barwidth = unit(2, "in"),
                             direction = "horizontal")
    ) +
    ggnewscale::new_scale_color() +
    geom_point(aes(color = pred_clust), size = 1, alpha = 0.8) +
    geom_point(data = year_centroids, 
               shape = 18,
               size = 2.5,
               color = "black",
               alpha = 0.85) +
    ggrepel::geom_text_repel(aes(label = Year),
                             year_centroids) +
    scale_color_brewer(
      palette = "Dark2",
      guide = guide_legend(override.aes = list(size = 2),
                           direction = "horizontal",
                           order = 1)
    ) +
    labs(color = "Predator cluster") +
    theme_classic(base_size = 10)
}

p <- map2(c(1, 1, 2), c(2, 3, 3), nmds_plot) %>% 
  reduce(`|`) +
  plot_annotation(tag_levels = 'A') +
  plot_layout(guides = "collect") &
    theme(legend.position = "bottom",
          legend.box = "vertical",
          legend.box.margin = margin(t = -3),
          legend.spacing.y = unit(-5, "pt"),
          plot.tag = element_text(face = "bold"))
ggsave(here::here("figs/Figure 6.eps"), p, 
       width = 169, height = 100, units = "mm")
p

@@

sublabels <- tibble(
  pred_clust = factor(levels(stations_clust$pred_clust)),
  labels = LETTERS[1:3],
  x = 1, y = 15
)
p <- ggplot(stations_clust, 
       aes(x = ice_coverage / 10, fill = after_stat(x))) + 
  geom_histogram(bins = 20, color = "grey30") +
  geom_vline(aes(xintercept = median_ice),
             median_coverge,
             color = "red", linetype = "dashed") +
  geom_text(aes(x = x, y = y, label = labels), sublabels, 
            hjust = 1, vjust = 1,
            fontface = "bold") +
  scale_x_continuous(labels = scales::percent) +
  scale_fill_distiller(palette = "Blues", guide = NULL) +
  facet_grid(rows = vars(pred_clust)) +
  labs(x = "Ice coverage",
       y = "# sites") +
  theme_classic() +
  theme(strip.text = element_blank())

ggsave(here::here("figs/Figure 3.eps"), p, 
       width = 169, height = 121, units = "mm")
p
